---
title: "A 26-year time series of mortality and growth of the Pacific oyster C. gigas recorded along French coasts"
subtitle: "Article submitted in Scientific data"
author: "This code was written by Anna Mazaleyrat, Laurent Dubroca and Julien Normand"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: yes
    code_folding: hide
    thumbnails: false
    lightbox: true
    number_section: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: console
  wrap: 120
  markdown: 
    wrap: 120
---

```{=html}
<style>
#toc ul.nav li ul li {
    display: none;
    max-height: none;
}

#toc ul.nav li.active ul li  {
    display: block;
    max-height: none;
}

#toc ul.nav li ul li ul li {
    max-height: none;
    display: none !important;
}

#toc ul.nav li ul li.active ul li {
    max-height: none;
    display: block !important;
}
</style>
```
```{r message=FALSE, warning=FALSE}
rm(list = ls())
library(nls.multstart)
library(broom)
library(purrr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
library(viridis)
library(DT)
library(formattable)
library(here)

theme_graphic <- function(base_family = "sans", ...) {
  theme_bw(base_family = base_family, ...) +
    theme(
      panel.grid = element_blank(),
      legend.background = element_rect(color = NA, fill = NA),
      strip.text = element_text(size = 11),
      axis.title = element_text(size = 12),
      plot.margin = margin(0, 0.1, 0.1, 0, "cm"),
      legend.text = element_text(size = 11),
      legend.title = element_text(size = 12),
      legend.key.height = unit(0.5, "cm"),
      legend.key.width = unit(0.5, "cm")
    )
}

operationnel <- TRUE
knitr::opts_chunk$set(
  warning = !operationnel,
  message = !operationnel,
  fig.width = 12,
  progress = !operationnel,
  verbose = !operationnel
)
```

The aim of the article was to model growth and cumulative mortality of spat and half-grown oysters as a function of
time, to cope with changes in data acquisition frequency, and produce standardized growth and cumulative mortality
indicators to improve data usability. To do so we relied on the nls.multstrat package:

> nls_multstart() is the main (currently only) function of nls.multstart. Similar to the R package nls2, it allows
> multiple starting values for each parameter and then iterates through multiple starting values, attempting a fit with
> each set of start parameters. The best model is then picked on AIC score. This results in a more reproducible and
> reliable method of fitting non-linear least squares regression in R.

```{r fig.height=10}
# Load of the clean data set.This data set is available on Zenodo (10.5281/zenodo.5744977).
growth_death <- read.csv(here("data/clean/DataResco_clean.csv"))

growth_death <-growth_death %>%
select(-num, -name, -zone_en, -lat, -long)

cols_to_make_factor <- growth_death %>%
  select(batch, site, classe_age, campaign) %>%
  colnames()

growth_death <- growth_death %>% mutate_at(cols_to_make_factor, factor)
growth_death$mean_CM <- as.numeric(growth_death$mean_CM)
growth_death$mean_mass <- as.numeric(growth_death$mean_mass)
growth_death$date <- as.Date(growth_death$date)
```

```{r echo=FALSE}
rm(cols_to_make_factor)
```

According to previous studies, mortality and growth curves in *C. gigas* follow a sigmoid curve. Therefore, we fitted a
logistic and a Gompertz model, which correspond to the most commonly used sigmoid models for growth and other data, to
describe mean mass and cumulative mortality at time x.

Logistic equation:

```{r}
Logistic <- function(a, b, c, x) {
  return(a / (1 + exp(-b * (x - c))))
}
Logistic
```

Gompertz equation:

```{r}
Gompertz <- function(a, b, c, x) {
  return(a * (exp(-exp(-b * (x - c)))))
}
Gompertz
```

These equations estimate three parameters:

-   the upper asymptote (a)

-   the slope at inflection (b)

-   the time of inflection (c)

Let's visualize the differences between the two equations:

```{r}
Logisticb <- function(param, x = 1:365) {
  a <- param[2]
  b <- param[1]
  c <- param[3]
  a / (1 + exp(-b * (x - c)))
}

Gompertzb <- function(param, x = 1:365) {
  a <- param[2]
  b <- param[1]
  c <- param[3]
  a * (exp(-exp(-b * (x - c))))
}

pipo1 <- data.frame(x = 1:365, y = Logisticb(c(0.05, 1, 150)), b = "0.05")
pipo2 <- data.frame(x = 1:365, y = Logisticb(c(0.1, 1, 150)), b = "0.1")
pipo3 <- data.frame(x = 1:365, y = Logisticb(c(1, 1, 150)), b = "1")
pipo123 <- rbind(pipo1, pipo2, pipo3)
pipo123$model <- as.factor(rep("Logistic"))

pipo4 <- data.frame(x = 1:365, y = Gompertzb(c(0.05, 1, 150)), b = "0.05")
pipo5 <- data.frame(x = 1:365, y = Gompertzb(c(0.1, 1, 150)), b = "0.1")
pipo6 <- data.frame(x = 1:365, y = Gompertzb(c(1, 1, 150)), b = "1")
pipo456 <- rbind(pipo4, pipo5, pipo6)
pipo456$model <- as.factor(rep("Gompertz"))

rbind(pipo123, pipo456) %>%
  ggplot(aes(x = x, y = y, colour = b)) +
  geom_line() +
  annotate("segment",
    x = 20, xend = 95, y = 1, yend = 1, arrow = arrow(), size = 1
  ) +
  geom_text(x = 5, y = 1, label = "a", color = "black", size = 5) +
  geom_vline(xintercept = 150, col = "black", linetype = "dashed") +
  geom_text(x = 155, y = 0, label = "c", color = "black", size = 5) +
  theme_bw() +
  labs(y = "f(x)", col = expression(b)) +
  facet_grid(~model)
```

```{r echo=FALSE}
rm(
  pipo1, pipo2, pipo3, pipo4, pipo5, pipo6, pipo123, pipo456, Logisticb,
  Gompertzb
)
```

# Study sites {#sites-link}

Here, we focus on 13 sites that were almost continuously monitored since 1993. All these sites stand in tidal areas
except Marseillan, located in the Mediterranean Thau lagoon, for which tidal variations are only tenuous and Men-er-Roué
which is in subtidal deep-water oyster culture area in the Bay of Quiberon.

```{r}
sites <- read.csv(here("data/raw/sites.csv"))
sites <- sites %>%
  mutate(site = as.factor(site), num = as.factor(paste(num)))

# reorganize the order of sites to later make figures
sites$num <- ordered(sites$num, levels = c("13", "12", "11", "10", "9", "8", "7", "6", "5", "4", "3", "2", "1"))

datatable(sites,
  rownames = FALSE,
  caption = "Table 1: Site identification and coordinates in WGS84",
  options = list(pageLength = 13, searching = FALSE)
)
```

# Life-cycle indicators of spat

## Mean mass

```{r fig.height=10}
N0_growth <- growth_death %>%
  select(-mean_CM) %>%
  drop_na() %>%
  filter(classe_age == "N0")

ggplot(data = N0_growth, aes(x = date_jj, y = mean_mass)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme(legend.position = "bottom")
```

To model the changes in mean mass, we needed to first find the starting values.

> Random start parameter values are picked from a uniform distribution between `start_lower()` and `start_upper()` for
> each parameter.

For mean mass of spat, we will set the `start_lower()` and `start_upper()` values as follows :

-   a (the upper asymptote) is between 0 and 110% of the maximum value observed at seeding date

-   b (slope at inflection) is between 0 and 0.1 (which is already a very sharp increase)

-   c (time of inflection) is visually estimated (in that case between 125 and 300)

Second, we can set `lower()` and `upper()` which represent the upper and lower boundaries for parameter estimates. These
will be fixed as follows :

-   a (the upper asymptote) is between 0 and 125% of the maximum value observed at seeding date

-   b (slope at inflection) is between 0 and 0.2

-   c (time of inflection) is between 0 and 365 (i.e. growth slows down before the end of the year)

```{r echo=FALSE}
# N0_growth %>%
#   group_by(site, campaign) %>%
#   filter(date == max(date)) %>%
#   ungroup() %>%
#   summarize(max(mean_mass))
```

```{r}
set.seed(1)
N0_growth_fits <- N0_growth %>%
  group_by(site, campaign) %>%
  tidyr::nest() %>%
  mutate(
    fits_Logistic = purrr::map(data, ~ nls_multstart(mean_mass ~ Logistic(a, b, c, x = date_jj),
      data = .x,
      iter = 5000,  # number of combinations of starting parameters which will be tried
      start_lower = c(a = 0, b = 0, c = 125),
      start_upper = c(a = 61, b = 0.1, c = 300),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,# The number of counts that the winning model should be undefeated for before it is 
      # declared the winner.
      lower = c(a = 0, b = 0, c = 0),
      upper = c(a = 70, b = 0.2, c = 365)
    )),
    fits_Gompertz = purrr::map(data, ~ nls_multstart(mean_mass ~ Gompertz(a, b, c, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 125),
      start_upper = c(a = 61, b = 0.1, c = 300),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0),
      upper = c(a = 70, b = 0.2, c = 365)
    ))
  )
```

We now check whether there are convergence issues

```{r}
N0_growth_fits %>%
  mutate(summary = map(fits_Logistic, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE")

N0_growth_fits %>%
  mutate(summary = map(fits_Gompertz, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE")
```

The dataframes are empty (one with logistic models that failed to converge and the other one with Gompertz models that
failed to converge). There are no convergence issues.

```{r echo=FALSE}
# growth_death %>%
#   group_by(campaign, site, classe_age) %>%
#   filter(date_jj == min(date_jj)) %>%
#   ungroup() %>%
#   summarize(median(date_jj)) %>%
#   as.numeric()
#
# growth_death %>%
#   group_by(campaign, site, classe_age) %>%
#   filter(date_jj == max(date_jj)) %>%
#   ungroup() %>%
#   summarize(median(date_jj)) %>%
#   as.numeric()
```

Let's see the if there is a good fit between observed (black circle) and predicted values (red and blue lines). We only
make prediction between Julian day 65 (median day of seeding date) and 337 (median day of the end of the monitoring).

```{r fig.height=10}
N0_growth_model_stack <- gather(N0_growth_fits, "model", "best_model", starts_with("fits")) %>%
  filter(!is.null(best_model)) %>%
  mutate(aic = map_dbl(best_model, possibly(AIC, otherwise = NA))) %>%
  mutate(model = case_when(model == "fits_Logistic" ~ "Logistic", model == "fits_Gompertz" ~ "Gompertz"))

to_predict <- N0_growth %>%
  do(data.frame(date_jj = seq(65, 337, by = 1), stringsAsFactors = FALSE))

N0_growth_preds <- N0_growth_model_stack %>%
  mutate(preds = map(best_model, augment, newdata = to_predict)) %>%
  unnest(preds)

N0_growth_preds %>%
  ggplot() +
  geom_line(aes(date_jj, .fitted, col = model), size = 1) +
  geom_point(data = N0_growth, aes(date_jj, mean_mass), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

Both models seems very good.

Let's see if the AIC was calculated for all of them.

```{r}
filter(N0_growth_model_stack, aic == "-Inf" | is.na(aic) | aic == "Inf")
```

Yes it was (data frame empty).

### Model selection

Let's find out which model (Gompertz or Logistic) is the best.

```{r fig.height=7}
N0_growth_aic_median <- N0_growth_model_stack %>%
  group_by(model) %>%
  summarise(median_aic = median(aic), count = n()) %>%
  ungroup()

Spat_growth <- ggplot() +
  geom_histogram(data = N0_growth_model_stack, aes(aic), alpha = 0.5, col = "black", bins = 60, fill = "#EE3B3B") +
  geom_vline(data = N0_growth_aic_median, aes(xintercept = median_aic), linetype = "dashed") +
  facet_wrap(model ~ ., ncol = 1, scales = "free") +
  theme_graphic() +
  ylab("Count") +
  xlab("AIC score") +
  geom_text(
    data = N0_growth_aic_median, aes(label = paste("Median AIC =", round(median_aic, 1)), x = -50, y = 35),
    col = "#EE3B3B", vjust = "inward", hjust = "inward"
  )

Table1 <- group_by(N0_growth_model_stack, site, campaign) %>%
  filter(aic == min(aic, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(model) %>%
  tally() %>%
  mutate(perc_best = round(n / sum(n) * 100)) %>%
  select(-n) %>%
  rename(Model = model) %>%
  rename("Percentage of lowest \nAIC score" = perc_best)
N0_growth_Table <- ggtexttable(Table1, rows = NULL, theme = ttheme("light"))

ggarrange(Spat_growth, N0_growth_Table, ncol = 1, heights = c(1, 0.35))
```

```{r echo=FALSE}
rm(N0_growth_aic_median, Table1, Spat_growth)
```

The logistic equation is better than the Gompertz one. For 81% of the year x site combinations, the logistic model has a
lower AIC than the Gompertz model.

### Best model (logistic)

Let's see the predicted values for the logistic models

```{r fig.height=10}
N0_growth_preds %>%
  filter(model == "Logistic") %>%
  ggplot() +
  geom_line(aes(date_jj, .fitted), size = 1, col = "#EE3B3B") +
  geom_point(data = N0_growth, aes(date_jj, mean_mass), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

The sites refer to [table 1](#sites-link)

We can also plot the residuals of the logistic models

```{r fig.height=10}
N0_growth_model_stack %>%
  filter(model == "Logistic") %>%
  mutate(preds = map(best_model, augment)) %>%
  unnest(preds) %>%
  select(-data, -model, -best_model) %>%
  ggplot(aes(date_jj, .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = 2) +
  facet_grid(site ~ campaign)
```

We can looked at the distribution and median of the parameters for the logistic model

```{r fig.height=10}
N0_growth_params <- N0_growth_model_stack %>%
  filter(model == "Logistic") %>%
  mutate(params = map(best_model, tidy)) %>%
  unnest(params) %>%
  select(-data, -best_model)

N0_growth_param_median <- N0_growth_params %>%
  group_by(site, term) %>%
  summarise(median = median(estimate), count = n()) %>%
  ungroup()

N0_growth_params %>%
  ggplot() +
  geom_density(aes(x = estimate, fill = term, ..scaled..), alpha = 0.3) +
  scale_fill_viridis(discrete = TRUE) +
  facet_grid(site ~ term, scales = "free") +
  geom_vline(data = N0_growth_param_median, aes(xintercept = median, col = term), size = 1.5) +
  scale_colour_viridis(discrete = TRUE) +
  theme_graphic()
```

Let's plot the raster of mean mass predicted:

```{r}
N0_growth_preds337 <- N0_growth_preds %>%
  filter(date_jj == "337" & model == "Logistic") %>%
  select(-model, -date_jj) %>%
  mutate(campaign = as.factor(campaign), variable = as.factor(rep("Growth")))

ggplot(N0_growth_preds337, aes(y = site, x = campaign, fill = .fitted)) +
  geom_raster() +
  coord_fixed() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white", size = 0.5, linetype = "solid"),
    legend.position = "bottom", panel.border = element_rect(fill = NA)
  ) +
  xlab("campaign") +
  ylab("Site") +
  scale_fill_viridis(direction = -1)
```

## Cumulative mortality {#github-link}

```{r fig.height=10}
N0_death <- growth_death %>%
  select(-mean_mass) %>%
  drop_na() %>%
  filter(classe_age == "N0")

ggplot(data = N0_death, aes(x = date_jj, y = mean_CM)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme(legend.position = "bottom")
```

```{r echo=FALSE}
# N0_death %>%
#   group_by(campaign, site) %>%
#   filter(date==max(date)) %>%
#   ungroup() %>%
#   summarize(max(mean_CM))
```

We set the `start_lower()` and `start_upper()` values for the parameters as follows :

-   a (the upper asymptote) is between 0 and 1

-   b (slope at inflection) is between 0 and 1

-   c (time of inflection) is visually estimated (in that case between 125 and 300)

We also set `lower()` and `upper()` which represent the upper and lower boundaries for parameter estimates. These are
fixed as follows :

-   a is between 0 and 1

-   b is between 0 and 1

-   c is between 0 and 365

```{r}
N0_death_fits <- N0_death %>%
  group_by(site, campaign) %>%
  tidyr::nest() %>%
  mutate(
    fits_Logistic = purrr::map(data, ~ nls_multstart(mean_CM ~ Logistic(a, b, c, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 125),
      start_upper = c(a = 1, b = 1, c = 300),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0),
      upper = c(a = 1, b = 1, c = 365)
    )),
    fits_Gompertz = purrr::map(data, ~ nls_multstart(mean_CM ~ Gompertz(a, b, c, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 125),
      start_upper = c(a = 1, b = 1, c = 300),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0),
      upper = c(a = 1, b = 1, c = 365)
    ))
  )
```

Let's see all the predictions for both models

```{r fig.height=10}
N0_death_model_stack <- gather(N0_death_fits, "model", "best_model", starts_with("fits")) %>%
  filter(!is.null(best_model)) %>%
  mutate(aic = map_dbl(best_model, possibly(AIC, otherwise = NA))) %>%
  mutate(model = case_when(model == "fits_Logistic" ~ "Logistic", model == "fits_Gompertz" ~ "Gompertz"))

N0_death_preds <- N0_death_model_stack %>%
  mutate(preds = map(best_model, augment, newdata = to_predict)) %>%
  unnest(preds) %>%
  # to later see the models for which AIC was not calculated
  mutate(aic_compiled = ifelse((aic == "-Inf" | aic == "Inf" | is.na(aic) == TRUE), "no", "yes")) %>%
  select(-data, -best_model) %>%
  mutate(model = as.factor(model))

ggplot() +
  geom_line(data = N0_death_preds, aes(date_jj, .fitted, col = model), size = 1) +
  geom_point(data = N0_death, aes(date_jj, mean_CM), alpha = 0.5) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

Everything looks good.

Let's see if some models failed to converge.

For the Logistic model :

```{r}
N0_death_info_Logistic <- N0_death_fits %>%
  mutate(summary = map(fits_Logistic, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE") %>%
  select(-data, -fits_Logistic, -fits_Gompertz, -finTol, -BIC)
N0_death_info_Logistic

failed_conv_log <- N0_death_info_Logistic %>%
  select(site, campaign) %>%
  mutate(model = rep("Logistic"))
```

Some models failed to converge.

For the Gompertz model :

```{r}
N0_death_info_Gompertz <- N0_death_fits %>%
  mutate(summary = map(fits_Gompertz, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE") %>%
  select(-data, -fits_Logistic, -fits_Gompertz, -finTol, -BIC)
N0_death_info_Gompertz

failed_conv_gomp <- N0_death_info_Gompertz %>%
  select(site, campaign) %>%
  mutate(model = rep("Gompertz"))

failed_conv_death_N0 <- rbind(failed_conv_log, failed_conv_gomp)
```

```{r}
rm(failed_conv_log, failed_conv_gomp, N0_death_info_Logistic, N0_death_info_Gompertz)
```

Some models failed to converge (around 30 for both the Gompertz and the logistic).

Let's see the predictions for those models.

```{r fig.height=10}
N0_death_model_failled_conv <- inner_join(N0_death_preds, failed_conv_death_N0, by = c("site", "campaign", "model"))

ggplot() +
  geom_line(data = N0_death_model_failled_conv, aes(date_jj, .fitted, col = model), size = 1) +
  geom_point(data = inner_join(N0_death, failed_conv_death_N0, by = c("site", "campaign")), aes(date_jj, mean_CM), alpha = 0.5) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

```{r echo=FALSE}
rm(failed_conv_death_N0, N0_death_model_failled_conv)
```

These models may have issues to converge because it may be difficult to estimate the time of inflection. However, the
upper asymptote should be correctly estimated even if the model do not converge. As were are mainly interested in
estimating the cumulative mortality at the end of the year, this lack of convergence is not an issue to reach our goal.

Now let's see if the AIC was computed for all models:

```{r}
filter(N0_death_model_stack, aic == "-Inf" | is.na(aic) == "TRUE" | aic == "Inf")
```

The AIC was not computed for only 2 models. Let's see if something look suspicious on the predicted mortality

```{r}
N0_failed_aic <- N0_death_preds %>%
  filter(aic_compiled == "no") %>%
  mutate(batch= paste(campaign, site, sep = "_"))

N0_failed_obs <- N0_death %>%
  mutate(batch= paste(campaign, site, sep = "_")) %>%
  filter(batch%in% N0_failed_aic$batch)

ggplot() +
  geom_line(data = N0_failed_aic, aes(x = date_jj, y = .fitted, col = aic_compiled, linetype = model), size = 1) +
  geom_point(data = N0_failed_obs, aes(x = date_jj, y = mean_CM), alpha = 0.5) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

```{r echo=FALSE}
rm(N0_failed_obs)
```

The AIC was not computed likely because the mortality is always equal to 0. It thus wanted to fir a sigmoid but the data
do not allow it. This is not an issue, both models are good.

### Model selection

```{r  fig.height=7}
# Stack without the models for which AIC was not computed or that failed to converge
N0_death_model_stack2 <- N0_death_model_stack %>%
  filter(!is.na(aic) & !aic == "-Inf" & !aic == "Inf")

N0_death_aic_median <- N0_death_model_stack2 %>%
  group_by(model) %>%
  summarise(median_aic = median(aic), count = n()) %>%
  ungroup()

Spat_mortality <- ggplot() +
  geom_histogram(data = N0_death_model_stack2, aes(aic), alpha = 0.5, col = "black", bins = 60, fill = "#EE3B3B") +
  geom_vline(data = N0_death_aic_median, aes(xintercept = median_aic), linetype = "dashed") +
  facet_wrap(. ~ model, ncol = 1) +
  theme_graphic() +
  ylab("Count") +
  xlab("AIC score") +
  geom_text(data = N0_death_aic_median, aes(
    label = paste("Median AIC =", round(median_aic, 1)),
    x = min(N0_death_model_stack2$aic), y = 70
  ), col = "#EE3B3B", vjust = "inward", hjust = "inward")

Table3 <- group_by(N0_death_model_stack2, site, campaign) %>%
  filter(aic == min(aic, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(model) %>%
  tally() %>%
  mutate(perc_best = round(n / sum(n) * 100)) %>%
  select(-n) %>%
  rename(Model = model) %>%
  rename("Percentage of lowest \nAIC score" = perc_best)
N0_death_Table <- ggtexttable(Table3, rows = NULL, theme = ttheme("light"))

ggarrange(Spat_mortality, N0_death_Table, ncol = 1, heights = c(1, 0.35))
```

```{r echo=FALSE}
rm(N0_death_aic_median, Table3, Spat_mortality, N0_death_model_stack, N0_failed_aic)
```

The best model is the Gompertz one.

### Best model (Gompertz)

```{r fig.height=10}
N0_death_preds %>%
  filter(model == "Gompertz") %>%
  ggplot() +
  geom_line(aes(date_jj, .fitted), size = 1, col = "#EE3B3B") +
  geom_point(data = N0_death, aes(date_jj, mean_CM), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw()
```

The sites refer to [table 1](#sites-link)

We can represent the median of the parameter (for the model that did not failed to converge)

```{r fig.height=10}
N0_death_params <- N0_death_model_stack2 %>%
  filter(model == "Gompertz") %>%
  mutate(params = map(best_model, tidy)) %>%
  unnest(params) %>%
  select(-data, -best_model)

N0_death_param_median <- N0_death_params %>%
  group_by(site, term) %>%
  summarise(median = median(estimate), count = n()) %>%
  ungroup()

N0_death_params %>%
  ggplot() +
  geom_density(aes(x = estimate, fill = term, ..scaled..), alpha = 0.3) +
  scale_fill_viridis(discrete = TRUE) +
  facet_grid(site ~ term, scales = "free") +
  geom_vline(data = N0_death_param_median, aes(xintercept = median, col = term), size = 1.5) +
  scale_colour_viridis(discrete = TRUE) +
  theme_graphic()
```

Let's plot the raster of mortality

```{r fig.height=10}
N0_death_preds337 <- N0_death_preds %>%
  filter(date_jj == "337" & model == "Gompertz") %>%
  select(-model, -date_jj, -aic_compiled) %>%
  mutate(campaign = as.factor(campaign), variable = as.factor(rep("Death")))

ggplot(N0_death_preds337, aes(y = site, x = campaign, fill = .fitted)) +
  geom_raster() +
  coord_fixed() +
  theme(
    panel.background = element_rect(fill = "white", colour = "white", size = 0.5, linetype = "solid"),
    legend.position = "bottom", panel.border = element_rect(fill = NA)
  ) +
  xlab("campaign") +
  ylab("Site") +
  scale_fill_viridis(direction = -1)
```

Now we can put on the same figure the cumulative mortality and growth of spat:

```{r figure2, fig.height=10}
N0_death_growth <- rbind(N0_death_preds337, N0_growth_preds337)

# Add information of the sites
# sites$num <- ordered(sites$num, levels = c("13", "12", "11", "10", "9", "8", "7", "6", "5", "4", "3", "2", "1"))

N0_death_growth <- merge(N0_death_growth, sites, by = "site", all.x = T)

N0_death_growth_graph <- ggplot() +
  coord_fixed() +
  geom_tile(data = subset(N0_death_growth, variable == "Death"), aes(x = campaign, y = num, fill = .fitted)) +
  geom_point(
    data = subset(N0_death_growth, variable == "Growth"), aes(x = campaign, y = num, size = .fitted),
    fill = "white", shape = 21
  ) +
  scale_fill_viridis(name = "Cumulative mortality predicted", direction = -1) +
  theme_graphic() +
  scale_size_continuous(name = "Mean mass predicted", breaks = c(15, 30, 45), label = c("15 g", "30 g", "45 g")) +
  ylab("Site") +
  xlab("") +
  theme(
    panel.background = element_rect(fill = "white", colour = "white", size = 0.5, linetype = "solid"),
    legend.position = "bottom", legend.box = "horizontal", plot.margin = unit(c(0, 0, 0, 0), "null")
  ) +
  guides(
    fill = guide_colourbar(
      title.position = "top", title.hjust = 0.5, frame.colour = "black", barwidth = 12,
      barheight = 1, order = 1
    ),
    size = guide_legend(title.position = "top", title.hjust = 0.5)
  )
N0_death_growth_graph
ggsave(here::here("figs/Fig2_spat_mortality_growth.png"), N0_death_growth_graph, width = 236, height = 138, dpi = 600, units = c("mm"))
```

The site refer to [table 1](#sites-link)

# Life-cycle indicators of half-grown oysters

## Mean mass

```{r fig.height=10}
J1_growth <- growth_death %>%
  select(-mean_CM) %>%
  drop_na() %>%
  filter(classe_age == "J1")

ggplot(data = J1_growth, aes(x = date_jj, y = mean_mass)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme(legend.position = "bottom")
```

As the mean mass of half-grown individuals at the beginning of the campaign was higher than 0, we fitted a
four-parameter version of the logistic and Gompertz models, which is common place in the growth-curve analysis of
bacterial counts. We estimated (d) which represents the lowest asymptote of the curve. This parameter also moves the
model curve vertically without changing its shape. The upper asymptote thus becomes equal to d + a.

Logistic equation:

```{r}
Logistic2 <- function(a, b, c, d, x) {
  return(d + (a / (1 + exp(-b * (x - c)))))
}

Logistic2
```

Gompertz equation:

```{r}
Gompertz2 <- function(a, b, c, d, x) {
  return(d + (a * (exp(-exp(-b * (x - c))))))
}
Gompertz2
```

```{r echo=FALSE}
# J1_growth %>%
#   group_by(site, campaign) %>%
#   filter(date == min(date)) %>%
#   ungroup() %>%
#   summarize(max(mean_mass))
#
# J1_growth %>%
#   group_by(site, campaign) %>%
#   filter(date == max(date)) %>%
#   ungroup() %>%
#   summarize(max(mean_mass))
```

The starting values for parameter b (slope at inflection) are the same as those for the spat. We set the `start_lower()`
and `start_upper()` values for the other parameters as follows :

-   c (time of inflection) is between 75 and 300

-   d (lowest asymptote) is between 0 and 110% of the maximum value at the seeding date

-   a is equal to 110 % of (the upper asymptote (a+ d) - the lowest asymptote (d)). a is thus equal to 123 - 54.3 = 69.
    110% of this values = 70.

We also set `lower()` and `upper()` which represent the upper and lower boundaries for parameter estimates. These are
fixed as follows :

-   c is between 0 and 365

-   d is between 0 and 125% of the maximum value at the seeding date

-   a is between 0 and 125% of (the upper asymptote - the lowest asymptote the maximum value). a is thus equal to 86

```{r}
J1_growth_fits <- J1_growth %>%
  select(site, campaign, date_jj, mean_mass) %>%
  group_by(site, campaign) %>%
  tidyr::nest() %>%
  mutate(
    fits_Logistic = purrr::map(data, ~ nls_multstart(mean_mass ~ Logistic2(a, b, c, d, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 75, d = 0),
      start_upper = c(a = 70, b = 0.1, c = 300, d = 60),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0, d = 0),
      upper = c(a = 86, b = 0.2, c = 365, d = 69)
    )),
    fits_Gompertz = purrr::map(data, ~ nls_multstart(mean_mass ~ Gompertz2(a, b, c, d, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 75, d = 0),
      start_upper = c(a = 70, b = 0.1, c = 300, d = 60),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0, d = 0),
      upper = c(a = 86, b = 0.2, c = 365, d = 69)
    ))
  )

# summary(J1_growth_fits$fits_Logistic[[3]])
# glance(J1_growth_fits$fits_Logistic[[3]])
```

```{r fig.height=10}
J1_growth_model_stack <- gather(J1_growth_fits, "model", "best_model", starts_with("fits")) %>%
  filter(!is.null(best_model)) %>%
  mutate(aic = map_dbl(best_model, possibly(AIC, otherwise = NA))) %>%
  mutate(model = case_when(model == "fits_Logistic" ~ "Logistic", model == "fits_Gompertz" ~ "Gompertz"))

J1_growth_preds <- J1_growth_model_stack %>%
  mutate(preds = map(best_model, augment, newdata = to_predict)) %>%
  unnest(preds) %>%
  mutate(aic_compiled = if_else(aic == "-Inf" | aic == "Inf" | is.na(aic) == TRUE, "no", "yes"))

J1_growth_preds %>%
  ggplot() +
  geom_line(aes(x = date_jj, y = .fitted, col = model)) +
  geom_point(data = J1_growth, aes(x = date_jj, y = mean_mass), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

The predictions looks good.

Let's see if some model failed to converge:

```{r}
J1_growth_fits %>%
  mutate(summary = map(fits_Logistic, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE")

J1_growth_fits %>%
  mutate(summary = map(fits_Gompertz, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE")
```

All models converged.

Let's see if the AIC was computed for all models:

```{r}
filter(J1_growth_model_stack, aic == "-Inf" | is.na(aic) == TRUE | aic == "Inf")
```

The AIC was not compiled for a lot of models (183 out of the 496 models). This is surprising since almost all models
converged. Let's try to find the origin of these "issues".

First, let's see if some predictions seem odd for the models for which AIC was not computed.

```{r fig.height=10}
J1_growth_failled_aic <- filter(J1_growth_preds, aic_compiled == "no") %>%
  select(site, campaign, model, date_jj, .fitted) %>%
  mutate(batch= paste(campaign, site, sep = "_"))

J1_failed_obs <- J1_growth %>%
  mutate(batch= paste(campaign, site, sep = "_")) %>%
  filter(batch%in% J1_growth_failled_aic$batch)

ggplot() +
  geom_line(data = J1_growth_failled_aic, aes(date_jj, .fitted, col = model), size = 1) +
  geom_point(data = J1_failed_obs, aes(date_jj, mean_mass), alpha = 0.5) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "none")
```

The predictions do not seem odd. Let's check the residuals of the models (here for the logistic models)

```{r fig.height=10}
filter(J1_growth_model_stack, model == "Logistic") %>%
  mutate(preds = map(best_model, augment)) %>%
  unnest(preds) %>%
  select(-data, -model, -best_model) %>%
  group_by(site, campaign) %>%
  mutate(aic_compiled = if_else(aic == "-Inf" | aic == "Inf" | is.na(aic) == TRUE, "no", "yes")) %>%
  filter(aic_compiled == "no") %>%
  ggplot() +
  geom_point(aes(date_jj, .resid, col = aic_compiled), alpha = 0.7) +
  geom_hline(yintercept = 0, linetype = 2) +
  facet_grid(site ~ campaign) +
  theme(legend.position = "none")
```

The AIC was not compiled for some models because there was a perfect fit (sum of residuals = 0) ! These models are thus
not problematic.

### Model selection

We now find out which model (Logistic or Gompertz) is the best.

```{r  fig.height=7}
J1_growth_model_stack2 <- J1_growth_model_stack %>%
  filter(!is.na(aic) == TRUE & !aic == "-Inf" & !aic == "Inf") 

J1_growth_aic_median <- J1_growth_model_stack2 %>%
  group_by(model) %>%
  summarise(median_aic = median(aic), count = n()) %>%
  ungroup()

Half_grown_growth <- ggplot() +
  geom_histogram(data = J1_growth_model_stack2, aes(aic), alpha = 0.5, col = "black", bins = 60, fill = "#1C86EE") +
  geom_vline(data = J1_growth_aic_median, aes(xintercept = median_aic), col = "#1C86EE", linetype = "dashed") +
  facet_grid(model ~ .) +
  theme_graphic() +
  ylab("Count") +
  xlab("AIC score") +
  geom_text(data = J1_growth_aic_median, aes(
    label = paste("Median AIC =", round(median_aic, 1)),
    x = -250, y = 35
  ), col = "#1C86EE", vjust = "inward", hjust = "inward")

Table2 <- group_by(J1_growth_model_stack2, site, campaign) %>%
  filter(aic == min(aic, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(model) %>%
  tally() %>%
  mutate(perc_best = round(n / sum(n) * 100)) %>%
  select(-n) %>%
  rename(Model = model) %>%
  rename("Percentage of lowest \nAIC score" = perc_best)
J1_growth_Table <- ggtexttable(Table2, rows = NULL, theme = ttheme("light"))

ggarrange(Half_grown_growth, J1_growth_Table, ncol = 1, heights = c(1, 0.35))
```

```{r echo=FALSE}
rm(Table2, J1_growth_aic_median, Half_grown_growth, J1_growth_failled_aic, J1_failed_obs)
```

The best model is the logistic one !

### Best model (logistic)

```{r fig.height=10}
J1_growth_preds %>%
  filter(model == "Logistic") %>%
  ggplot() +
  geom_line(aes(date_jj, .fitted), size = 1, col = "#1C86EE") +
  geom_point(data = J1_growth, aes(date_jj, mean_mass), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw()
```

The sites refer to [table 1](#sites-link)

We can represent the parameters of the the best models

```{r fig.height=10}
J1_growth_model_stack2$campaign <- as.numeric(paste(J1_growth_model_stack2$campaign))

J1_growth_params <- J1_growth_model_stack2 %>%
  filter(model == "Logistic") %>%
  mutate(params = map(best_model, tidy)) %>%
  unnest(params) %>%
  select(-data, -best_model) %>%
  mutate(site = as.factor(site))

J1_growth_params_median <- J1_growth_params %>%
  group_by(term, site) %>%
  summarise(median = median(estimate)) %>%
  mutate(site = as.factor(site))

ggplot() +
  geom_density(data= J1_growth_params, aes(x = estimate, fill = site, ..scaled..), alpha = 0.3) +
  scale_fill_viridis(discrete = TRUE) +
  facet_grid(site ~ term, scales = "free") +
  geom_vline(data = J1_growth_params_median, aes(xintercept = median, col = site), size = 1.5) +
  scale_colour_viridis(discrete = TRUE) +
  theme_graphic()
```

```{r echo=FALSE}
rm(J1_growth_params_median, J1_growth_params, J1_growth_model_stack)
```

For the half-grown, as the mass at the beginning of the monitoring is higher than 0, it makes little sense to represent
the mass at the end of the campaign since it depend on the initial mass. We thus decided to represent the growth ratio
(mass at the Julian day 337 divided by mass at Julian day 65)

```{r fig.height=10}
J1_growth_preds337_65 <- J1_growth_preds %>%
  filter(model == "Logistic" & (date_jj == "65" | date_jj == "337")) %>%
  select(-aic, -model, -aic_compiled) %>%
  reshape2::dcast(campaign + site ~ date_jj, value = .fitted) %>%
  rename("pred65" = "65", "pred337" = "337") %>%
  mutate(increase = pred337 / pred65) 

ggplot() +
  coord_fixed() +
  geom_tile(data = J1_growth_preds337_65, aes(campaign, site, fill = increase)) +
  scale_fill_viridis(name = "Growth ratio", direction = -1) +
  theme_graphic() +
  theme(legend.position = "bottom")
```

## Cumulative mortality

```{r}
J1_death <- growth_death %>%
  select(-mean_mass) %>%
  drop_na() %>%
  filter(classe_age == "J1")
```

```{r fig.height=10}
ggplot(data = J1_death, aes(x = date_jj, y = mean_CM)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme(legend.position = "bottom")
```

The `start_lower()` and `start_upper()` values as well as the `lower()` and `upper()` boundaries were almost the same
than those for the spat (you can see them [here](#github-link)). The only difference is that `start_upper()` and
`upper()` were respectively 0.1 and 0.2 comapred to 1 and 1 for spat.

```{r}
J1_death_fits <- J1_death %>%
  group_by(site, campaign) %>%
  tidyr::nest() %>%
  mutate(
    fits_Logistic = purrr::map(data, ~ nls_multstart(mean_CM ~ Logistic(a, b, c, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 125),
      start_upper = c(a = 1, b = 0.1, c = 300),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0),
      upper = c(a = 1, b = 0.2, c = 365)
    )),
    fits_Gompertz = purrr::map(data, ~ nls_multstart(mean_CM ~ Gompertz(a, b, c, x = date_jj),
      data = .x,
      iter = 5000,
      start_lower = c(a = 0, b = 0, c = 125),
      start_upper = c(a = 1, b = 0.1, c = 300),
      supp_errors = "Y",
      na.action = na.omit,
      convergence_count = 200,
      lower = c(a = 0, b = 0, c = 0),
      upper = c(a = 1, b = 0.2, c = 365)
    ))
  )
```

```{r fig.height=10}
J1_death_model_stack <- gather(J1_death_fits, "model", "best_model", starts_with("fits")) %>%
  filter(!is.null(best_model)) %>%
  mutate(aic = map_dbl(best_model, possibly(AIC, otherwise = NA))) %>%
  mutate(model = case_when(model == "fits_Logistic" ~ "Logistic", model == "fits_Gompertz" ~ "Gompertz"))

J1_death_preds <- J1_death_model_stack %>%
  mutate(preds = map(best_model, augment, newdata = to_predict)) %>%
  unnest(preds) %>%
  select(-data, -best_model, -aic)

J1_death_preds %>%
  ggplot() +
  geom_line(aes(x = date_jj, y = .fitted, col = model), size = 1) +
  geom_point(data = J1_death, aes(x = date_jj, y = mean_CM), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

Predictions looks good. Are there some convergence issues ?

For the Logistic model:

```{r}
J1_death_info_Logistic <- J1_death_fits %>%
  mutate(summary = map(fits_Logistic, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE") %>%
  select(-data, -fits_Logistic, -fits_Gompertz, -finTol)
J1_death_info_Logistic

failed_conv_log <- J1_death_info_Logistic %>%
  select(site, campaign) %>%
  mutate(model = rep("Logistic"))
```

Few convergence issues.

For the Gompertz models :

```{r}
J1_death_info_Gompertz <- J1_death_fits %>%
  mutate(summary = map(fits_Gompertz, glance)) %>%
  unnest(summary) %>%
  filter(isConv == "FALSE") %>%
  select(-data, -fits_Logistic, -fits_Gompertz, -finTol)
J1_death_info_Gompertz

failed_conv_gomp <- J1_death_info_Gompertz %>%
  select(site, campaign) %>%
  mutate(model = rep("Gompertz"))

failed_conv_death_J1 <- rbind(failed_conv_log, failed_conv_gomp)
```

```{r echo=FALSE}
rm(failed_conv_log, failed_conv_gomp, J1_death_info_Logistic, J1_death_info_Gompertz)
```

Some models failed to converge. Around 10 for both models. Let's visualize the models that failed to converge:

```{r fig.height=10}
J1_death_model_failled_conv <- inner_join(J1_death_preds, failed_conv_death_J1, by = c("site", "campaign", "model"))

ggplot() +
  geom_line(data = J1_death_model_failled_conv, aes(x = date_jj, y = .fitted, col = model), size = 1) +
  geom_point(data = inner_join(J1_death, failed_conv_death_J1,
    by = c("site", "campaign")),
    aes(x = date_jj, y = mean_CM), alpha = 0.5
  ) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw() +
  theme(legend.position = "bottom")
```

Everything looks good. We now see if the AIC was computed for all models

```{r}
filter(J1_death_model_stack, is.na(aic) == TRUE | aic == "Inf" | aic == "-Inf")
```

The AIC was not compiled for GEFOS in 1998. Let's see the prediction

```{r fig.height=5}
J1_death_preds %>%
  filter(site == "GEFOS" & campaign == "1998") %>%
  ggplot() +
  geom_line(aes(x = date_jj, y = .fitted, col = model), size = 1) +
  geom_point(data = subset(J1_death, site == "GEFOS" & campaign == "1998"), aes(x = date_jj, y = mean_CM), alpha = 0.7) +
  theme_bw()
```

AIC was not computed because there is a perfect fit.

### Model selection

We now select the best model

```{r  fig.height=7}
J1_death_model_stack2 <- J1_death_model_stack %>%
  filter(!is.na(aic) == TRUE & !aic == "-Inf" & !aic == "Inf") 

J1_death_aic_median <- J1_death_model_stack2 %>%
  group_by(model) %>%
  summarise(median_aic = median(aic), count = n()) %>%
  ungroup()

Half_grown_mortality <- ggplot() +
  geom_histogram(data = J1_death_model_stack2, aes(aic), alpha = 0.5, col = "black", bins = 60, fill = "#1C86EE") +
  geom_vline(data = J1_death_aic_median, aes(xintercept = median_aic), linetype = "dashed") +
  facet_grid(model ~ .) +
  ylab("Count") +
  xlab("AIC score") +
  theme_graphic() +
  geom_text(
    data = J1_death_aic_median, aes(label = paste("Median AIC =", round(median_aic, 1)), x = -1300, y = 100),
    col = "#1C86EE"
  )

Table4 <- group_by(J1_death_model_stack2, site, campaign) %>%
  filter(aic == min(aic, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(model) %>%
  tally() %>%
  mutate(perc_best = round(n / sum(n) * 100)) %>%
  select(-n) %>%
  rename(Model = model) %>%
  rename("Percentage of lowest \nAIC score" = perc_best)
J1_death_Table <- ggtexttable(Table4, rows = NULL, theme = ttheme("light"))

ggarrange(Half_grown_mortality, J1_death_Table, ncol = 1, heights = c(1, 0.35))
```

```{r echo=FALSE}
rm(J1_death_aic_median, Half_grown_mortality, Table4, J1_death_model_failled_conv)
```

The Gompertz model is the best

### Best model (Gompertz)

```{r fig.height=10}
J1_death_preds %>%
  filter(model == "Gompertz") %>%
  ggplot() +
  geom_line(aes(date_jj, .fitted), size = 1, col = "#1C86EE") +
  geom_point(data = J1_death, aes(date_jj, mean_CM), alpha = 0.7) +
  facet_grid(site ~ campaign, scale = "free_y") +
  theme_bw()
```

The sites refer to [table 1](#sites-link)

```{r figure4, fig.height=10}
J1_death_params <- J1_death_model_stack2 %>%
  filter(model == "Gompertz") %>%
  mutate(params = map(best_model, tidy)) %>%
  unnest(params) %>%
  select(-data, -best_model) %>% 
  mutate(site = as.factor(site))

J1_death_params_median <- J1_death_params %>%
  group_by(term, site) %>%
  summarise(median = median(estimate), count = n()) %>%
  mutate(site = as.factor(site))

sites$num <- ordered(sites$num, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13"))

J1_death_params2 <- merge(J1_death_params, sites, by = "site", all.x = T)
J1_death_params_median2  <- merge(J1_death_params_median , sites, by = "site", all.x = T)

graph_J1_death_param <- ggplot() +
  geom_density(data = J1_death_params2, aes(x = estimate, fill = num, ..scaled..), alpha = 0.3) +
  scale_fill_viridis(discrete = TRUE) +
  facet_grid(num ~ term, scales = "free") +
  geom_vline(data= J1_death_params_median2, aes(xintercept = median, col = num), size = 1.5) +
  scale_colour_viridis(discrete = TRUE) +
  theme_graphic()+
  theme(legend.position="none")+
  ylab("Scale density")+
  xlab("Estimate")
graph_J1_death_param
ggsave(here("figs/Fig4_half_grown_mortality_param.png"), graph_J1_death_param, width = 210, height = 250, dpi = 600, units = c("mm"))
```

```{r echo=FALSE}
rm(J1_death_params_median, J1_death_params, J1_death_model_stack)
```

We now put the mean mass and mortality of half-grown on the same figure

```{r figure3, fig.height=10}
J1_death_preds337 <- J1_death_preds %>%
  filter(date_jj == "337" & model == "Gompertz") %>%
  select(-model) %>%
  reshape2::dcast(campaign + site ~ date_jj, value = .fitted) %>%
  rename(".fitted" = "337") %>%
  mutate(variable = rep("Death"))

J1_growth_preds337_65$variable <- rep("Growth")
J1_growth_preds337_65 <- J1_growth_preds337_65 %>%
  select(-pred65, -pred337) %>%
  rename(".fitted" = "increase")

J1_death_growth <- rbind(J1_death_preds337, J1_growth_preds337_65)
sites$num <- ordered(sites$num, levels = c("13", "12", "11", "10", "9", "8", "7", "6", "5", "4", "3", "2", "1"))

J1_death_growth <- merge(J1_death_growth, sites, by = "site", all.x = T)

J1_death_growth_graph <- ggplot() +
  coord_fixed() +
  geom_tile(data = subset(J1_death_growth, variable == "Death"), aes(campaign, num, fill = .fitted)) +
  geom_point(
    data = subset(J1_death_growth, variable == "Growth"), aes(campaign, num, size = .fitted),
    fill = "white", shape = 21
  ) +
  scale_fill_viridis(
    name = "Cumulative mortality predicted", limits = c(0, 0.73), breaks = c(0.0, 0.2, 0.4, 0.6),
    direction = -1
  ) +
  theme_graphic() +
  scale_size_continuous(name = "Growth ratio", breaks = c(2, 3, 4, 5), label = c("2", "3", "4", "5")) +
  xlab("") +
  ylab("Site") +
  theme(
    panel.background = element_rect(fill = "white", colour = "white", size = 0.5, linetype = "solid"),
    legend.position = "bottom", legend.box = "horizontal", plot.margin = unit(c(0, 0, 0, 0), "null")
  ) +
  guides(
    fill = guide_colourbar(
      title.position = "top", title.hjust = 0.5, frame.colour = "black", barwidth = 12, barheight = 1, order = 1
    ),
    size = guide_legend(title.position = "top", title.hjust = 0.5)
  )
J1_death_growth_graph

ggsave(here::here("figs/Fig3_half_grown_mortality_growth.png"), J1_death_growth_graph, width = 236, height = 138, dpi = 600, units = c("mm"))
```

# Technical validation

## Mean mass of oysters

```{r figure5, fig.height=10}
N0_growth_best_model <- N0_growth_preds %>%
  filter(model == "Logistic") %>%
  select(site, campaign, date_jj, .fitted) %>%
  mutate(classe_age = as.factor("N0"))

N0_J1_growth_preds <- J1_growth_preds %>%
  filter(model == "Logistic") %>%
  select(site, campaign, date_jj, .fitted) %>%
  mutate(classe_age = as.factor("J1")) %>%
  bind_rows(N0_growth_best_model, .)

sites$num <- ordered(sites$num, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13"))

N0_J1_growth_preds <- merge(N0_J1_growth_preds, sites, by = "site", all.x = T)

N0_J1_growth <- rbind(N0_growth, J1_growth)
N0_J1_growth <- merge(N0_J1_growth, sites, by = "site")

Growth_graphique_validation <-
  ggplot() +
  geom_point(data = N0_J1_growth, aes(date_jj, mean_mass), alpha = 0.6, size = 1.2) +
  geom_line(data = N0_J1_growth_preds, aes(date_jj, .fitted, col = classe_age), size = 0.5) +
  scale_x_continuous(limits = c(46, 365), guide = guide_axis(n.dodge = 2)) +
  facet_grid(num ~ campaign, scale = "free_y") +
  scale_color_manual(name = "Age classes", labels = c("Spat", "Half-grown"), values = c("#EE3B3B", "#1C86EE")) +
  theme_graphic() +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 0), "null")) +
  xlab("Julian day") +
  ylab("Mean mass of oysters (g)")
Growth_graphique_validation
ggsave(here::here("figs/Fig5_growth_validation.png"), Growth_graphique_validation, width = 315, height = 184, dpi = 400, units = c("mm"))
```

The sites refer to [table 1](#sites-link)

## Cumulative mortality of oysters

```{r figure6, fig.height=10}
N0_death_best_model <- N0_death_preds %>%
  filter(model == "Gompertz") %>%
  select(-aic_compiled, -aic) %>%
  mutate(classe_age = rep("N0"))

N0_J1_death_preds <- J1_death_preds %>%
  filter(model == "Gompertz") %>%
  mutate(classe_age = rep("J1")) %>%
  bind_rows(N0_death_best_model, .) %>%
  mutate(classe_age = as.factor(classe_age))

N0_J1_death_preds <- merge(N0_J1_death_preds, sites, by = "site")

N0_J1_death <- rbind(N0_death, J1_death)
N0_J1_death <- merge(N0_J1_death, sites, by = "site")

death_graphique_validation <-
  ggplot() +
  geom_point(data = N0_J1_death, aes(date_jj, mean_CM), alpha = 0.6, size = 1.2) +
  geom_line(data = N0_J1_death_preds, aes(date_jj, .fitted, col = classe_age), size = 0.5) +
  scale_x_continuous(limits = c(46, 365), guide = guide_axis(n.dodge = 2)) +
  scale_color_manual(name = "Age classes", labels = c("Spat", "Half-grown"), values = c("#EE3B3B", "#1C86EE")) +
  facet_grid(num ~ campaign, scale = "free_y") +
  theme_graphic() +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 0), "null")) +
  xlab("Julian day") +
  ylab("Cumulative mortality of oysters")
death_graphique_validation
ggsave(here::here("figs/Fig6_death_validation.png"), death_graphique_validation, width = 315, height = 184, dpi = 400, units = c("mm"))
```

The sites refer to [table 1](#sites-link)

## Model selection

```{r, figure7, fig.height=12}
# for growth
N0_growth_model_stack <- N0_growth_model_stack %>%
  select(site, campaign, aic, model) %>%
  mutate(species = as.factor(rep("Spat")))

J1_growth_model_stack2 <- J1_growth_model_stack2 %>%
  select(site, campaign, aic, model) %>%
  mutate(species = as.factor(rep("Half-grown"))) %>%
  mutate(campaign = as.factor(campaign))

growth_model_stack <- rbind(N0_growth_model_stack, J1_growth_model_stack2)
growth_model_stack$species <- relevel(growth_model_stack$species, ref = "Spat")

growth_aic_median <- growth_model_stack %>%
  group_by(species, model) %>%
  summarise(median_aic = median(aic), count = n()) %>%
  ungroup()

model_selection_growth <- ggplot() +
  geom_histogram(data = growth_model_stack, aes(aic, fill = species), alpha = 0.5, col = "black", bins = 60) +
  geom_vline(data = growth_aic_median, aes(xintercept = median_aic), linetype = "dashed") +
  theme_graphic() +
  ylab("Count") +
  xlab("AIC score") +
  ggtitle("a. Growth") +
  geom_text(data = growth_aic_median, aes(
    col = species, label = paste("Median AIC =", round(median_aic, 1)),
    x = c(-58, -58, -250, -250), y = 30
  ), vjust = "inward", hjust = "inward") +
  facet_grid(model ~ species, scales = "free") +
  scale_fill_manual(name = "Age classes", labels = c("Spat", "Half-grown"), values = c("#EE3B3B", "#1C86EE")) +
  scale_color_manual(name = "Age classes", labels = c("Spat", "Half-grown"), values = c("#EE3B3B", "#1C86EE")) +
  theme(legend.position = "none")

Table_growth_validaion <- ggarrange(N0_growth_Table, J1_growth_Table, ncol = 2)
model_growth_validation <- ggarrange(model_selection_growth, Table_growth_validaion, ncol = 1, heights = c(1, 0.35))

# For death
N0_death_model_stack2$species <- rep("Spat")
J1_death_model_stack2$species <- rep("Half-grown")
death_model_stack <- rbind(N0_death_model_stack2, J1_death_model_stack2)
death_model_stack$species <- as.factor(death_model_stack$species)
death_model_stack$species <- relevel(death_model_stack$species, ref = "Spat")

death_aic_median <- death_model_stack %>%
  group_by(model, species) %>%
  summarise(median_aic = median(aic), count = n()) %>%
  ungroup()

model_selection_death <- ggplot() +
  geom_histogram(data = death_model_stack, aes(aic, fill = species), alpha = 0.5, col = "black", bins = 60) +
  geom_vline(data = death_aic_median, aes(xintercept = median_aic), linetype = "dashed") +
  theme_graphic() +
  ylab("Count") +
  xlab("AIC score") +
  ggtitle("b. Mortality") +
  geom_text(data = death_aic_median, aes(
    col = species, label = paste("Median AIC =", round(median_aic, 1)),
    x = c(-1500, -1850, -1500, -1850), y = 100
  ), vjust = "inward", hjust = "inward") +
  facet_grid(model ~ species, scales = "free") +
  scale_fill_manual(name = "Age classes", labels = c("Spat", "Half-grown"), values = c("#EE3B3B", "#1C86EE")) +
  scale_color_manual(name = "Age classes", labels = c("Spat", "Half-grown"), values = c("#EE3B3B", "#1C86EE")) +
  theme(legend.position = "none")

Table_death_validation <- ggarrange(N0_death_Table, J1_death_Table, ncol = 2)

model_death_validation <- ggarrange(model_selection_death, Table_death_validation, ncol = 1, heights = c(1, 0.35))

# Merge the plot of growth and death
Table_validation_complete <- ggarrange(model_growth_validation, model_death_validation, nrow = 2)
Table_validation_complete
ggsave(here::here("figs/Fig7_model_validation.png"), Table_validation_complete, width = 210, height = 250, dpi = 400, units = c("mm"))
```

```{r}
# We now save the prediction
N0_J1_growth_preds <- N0_J1_growth_preds %>%
  select(-zone_fr) %>%
  rename("mass_pred" = ".fitted")

N0_J1_death_preds <- N0_J1_death_preds %>%
  select(-model, -zone_fr) %>%
  rename("CM_pred" = ".fitted")

complete_pred <- full_join(N0_J1_death_preds, N0_J1_growth_preds, by = c("site", "campaign", "date_jj", "classe_age", "num", "name", "zone_en", "lat", "long"))

complete_pred$mass_pred <- formattable(complete_pred$mass_pred, digits = 2, format = "f")
complete_pred$CM_pred <- formattable(complete_pred$CM_pred, digits = 3, format = "f")

# reorder column
complete_pred <- complete_pred[, c(6,1,7,8,9,10,2,5,3,4,11)]

write.csv(complete_pred, here::here("data/clean/DataResco_predicted.csv"), row.names = FALSE, quote = TRUE, na = "NA")
# This data set is available on Zenodo (10.5281/zenodo.5744977)
```

```{r echo=FALSE}
sessionInfo()
```
